Timing and magnitude of climate driven range shifts in transboundary fish stocks challenge their management

### 2021-07-26 Scripts/Manuscript.Rmd
flaged changes

**Our results suggest that 4,119 transboundary stocks will experience a range shift beyond historical variability by 2100 (hereafter referred to as ‘shifts’; Fig. \@ref(fig:toeFigure1)A), using a two s.d. threshold (i.e., representing a probability of 95% that the stock has shifted). This corresponds to 45% of the studied stocks (Fig. \@ref(fig:toeFigure1)C). Using a less conservative threshold (i.e., 1 s.d. representing a probability of 68% that the stock has shifted) results in 33% (n = 5,745) more shifting stocks, that is 63% of all studied stocks (Figs. \@ref(fig:toeFigureS2) and \@ref(fig:toeFigureS8)). For both cases, the first shift is modelled to have occurred back in 2006. The average year of shift in the shared distribution of these stocks in all EEZs analyzed is projected to be between 2029 $\pm$ 27 years (1 s.d. threshold) and 2036 $\pm$ 28 years (2 s.d. threshold). Furthermore, between 81% and 83% of the world’s EEZs will experience at least one transboundary stock shift by 2100 with 77% to 80% recording a distributional shift in stocks by the UN 2030 Agenda’s deadline (Fig. \@ref(fig:toeFigure1)C).**

>>>>

**Our results suggest that 4,119 transboundary stocks will experience a range shift beyond historical variability by 2100 (hereafter referred to as ‘shifts’; Fig. \@ref(fig:toeFigure1)A), using a two s.d. threshold (i.e., representing a probability of 95% that the stock has shifted). This corresponds to 45% of the studied stocks (Fig. \@ref(fig:toeFigure1)C). Using a less conservative threshold (i.e., one s.d. representing a probability of 68% that the stock has shifted) results in 33% (n = 5,745) more shifting stocks, that is, 63% of all studied stocks (Figs. \@ref(fig:toeFigureS2) and \@ref(fig:toeFigureS8)). For both cases, the first shift is modelled to have occurred back in 2006. The average year of shift in the shared distribution of these stocks in all EEZs analyzed is projected to be between 2029 $\pm$ 27 years (one s.d. threshold) and 2036 $\pm$ 28 years (two s.d. threshold). Furthermore, between 81% and 83% of the world’s EEZs will experience at least one transboundary stock shift by 2100 with 77% to 80% of EEZs recording a distributional stocks shift by the UN 2030 Agenda’s deadline (Fig. \@ref(fig:toeFigure1)C).**
